Sustainable computational science:\\ the ReScience initiative

### 2017-11-09 draft.tex
Mention popularity of Python and R
Mini-statistics on the review process
Update some numbers

ReScience is an openly-peer-reviewed journal that targets computational research
and encourages the explicit replication of already published research. In order
to provide the largest possible benefit to the scientific community, replications are
required to be reproducible and open-source. In less than two years of existence, 12
articles have been published and 3 are currently under review
(\href{https://github.com/ReScience/ReScience-submission/pull/20}{\#20},
\href{https://github.com/ReScience/ReScience-submission/pull/27}{\#27},
\href{https://github.com/ReScience/ReScience-submission/pull/30}{\#30}). The
editorial board covers a wide range of computational sciences (see
\url{http://rescience.github.io/board/}) and more than 70 volunteers have registered to be reviewers. The scientific domains of published work
are computational neuroscience, neuroimaging, computational ecology and
computer graphics, with a majority in computational neuroscience. There is a
strong bias towards successful replication (100\%); experience has
taught us that researchers are reluctant to publish failed replications, even when they can prove that the original work is wrong. For young researchers,
there is a social/professional risk in publishing articles that show
results from a senior researcher to be wrong. Until we implement a
certified anonymized submission process, this strong bias will most likely
remain.\\

>>>>

ReScience is an openly-peer-reviewed journal that targets computational research
and encourages the explicit replication of already published research. In order
to provide the largest possible benefit to the scientific community, replications are
required to be reproducible and open-source. In two years of existence, 17
articles have been published and 4 are currently under review
(\href{https://github.com/ReScience/ReScience-submission/pull/20}{\#20},
\href{https://github.com/ReScience/ReScience-submission/pull/27}{\#39},
\href{https://github.com/ReScience/ReScience-submission/pull/30}{\#41},
\href{https://github.com/ReScience/ReScience-submission/pull/30}{\#43}). The
editorial board covers a wide range of computational sciences (see
\url{http://rescience.github.io/board/}) and more than 70 volunteers have registered to be reviewers. The scientific domains of published work
are computational neuroscience, neuroimaging, computational ecology and
computer graphics, with a majority in computational neuroscience. The most
popular programming languages are Python and R. The review process takes about 100~days on average and involves about 50~comments. There is a
strong bias towards successful replication (100\%); experience has
taught us that researchers are reluctant to publish failed replications, even when they can prove that the original work is wrong. For young researchers,
there is a social/professional risk in publishing articles that show
results from a senior researcher to be wrong. Until we implement a
certified anonymized submission process, this strong bias will most likely
remain.\\
